Paper_Figure

### 2023-10-20 Marker_identfication_benchmark.Rmd

## Seurat v3 Wilcoxon unfiltered
Genes were ranked by their lowest adjusted P-value in any cluster (increasing order), if two genes had the same, prioritize genes with larger FC.
```{r}
tiss <- FindNeighbors(tiss, dims = 1:n_dim)
tiss <- FindClusters(tiss, resolution = 1.5, algorithm = 3)
method = "wilcox_no_filter"
marker <- FindAllMarkers(tiss, features = rownames(dat), only.pos = FALSE, test.use = "wilcox", logfc.threshold = 0, min.pct = 0)
gene_rank = marker %>% arrange(.,p_val_adj,desc(avg_log2FC)) %>% distinct(.,gene, .keep_all = TRUE) %>% select(gene)
gene_rank$'rank' = 1:nrow(gene_rank)
marker <- merge(marker,gene_rank,by = "gene")
write.table(marker,file = sprintf("%s%s_%s.csv",path,method,tissue_name),row.names = TRUE)
```
## Seurat v3 default
Genes were ranked by their lowest adjusted P-value in any cluster (increasing order), if two genes had the same, prioritize genes with larger FC.
```{r}
tiss <- FindNeighbors(tiss, dims = 1:n_dim)
tiss <- FindClusters(tiss, resolution = 1.5, algorithm = 3)

method = "wilcox_default"
marker <- FindAllMarkers(tiss, features = rownames(dat), only.pos = FALSE, test.use = "wilcox", logfc.threshold = 0.25,min.pct = 0.1)

@@

result = MarcoPolo.find_markers(adata=adata, regression_result=regression_result)
```
```{r}
method = "marcopolo"
marker = reticulate::py$result
marker$'rank' = marker$MarcoPolo_rank
write.table(marker,file = sprintf("%s%s_%s.csv",path,method,tissue_name),row.names = TRUE)
```

>>>>

## Seurat v3 Wilcoxon unfiltered
Genes were ranked by their lowest adjusted P-value in any cluster (increasing order), if two genes had the same, prioritize genes with larger FC.
```{r}
tiss <- FindNeighbors(tiss, dims = 1:n_dim)
tiss <- FindClusters(tiss, resolution = 1.5, algorithm = 3)
method = "wilcox_no_filter"
marker <- FindAllMarkers(tiss, features = selected_genes, only.pos = FALSE, test.use = "wilcox", logfc.threshold = 0, min.pct = 0)
gene_rank = marker %>% arrange(.,p_val_adj,desc(avg_log2FC)) %>% distinct(.,gene, .keep_all = TRUE) %>% select(gene)
gene_rank$'rank' = 1:nrow(gene_rank)
marker <- merge(marker,gene_rank,by = "gene")
write.table(marker,file = sprintf("%s%s_%s.csv",path,method,tissue_name),row.names = TRUE)
```
## Seurat v3 default
Genes were ranked by their lowest adjusted P-value in any cluster (increasing order), if two genes had the same, prioritize genes with larger FC.
```{r}
tiss <- FindNeighbors(tiss, dims = 1:n_dim)
tiss <- FindClusters(tiss, resolution = 1.5, algorithm = 3)

method = "wilcox_default"
marker <- FindAllMarkers(tiss, features = selected_genes, only.pos = FALSE, test.use = "wilcox", logfc.threshold = 0.25,min.pct = 0.1)

@@

result = MarcoPolo.find_markers(adata=adata, regression_result=regression_result)
```
```{r}
method = "marcopolo"
marker = reticulate::py$result
marker$'rank' = marker$MarcoPolo_rank + 1
write.table(marker,file = sprintf("%s%s_%s.csv",path,method,tissue_name),row.names = TRUE)
```

### 2023-10-20 paper_figure.Rmd

df_benchmark = read.table(paste0(path,tissue_name,"_benchmark_rank_table.csv"))
method_ls = colnames(df_benchmark)
method_fullname = setNames(c("LMD","singleCellHaystack","Hotspot","Marcopolo","SEMITONES","Seurat v3 default", "Seurat v3 Wilcoxon unfiltered","HighlyVariableGenes"),method_ls)
coldef = setNames(
  colorRampPalette(brewer.pal(7, "Set1"))(length(method_fullname)),
  method_fullname)
```
```{r}
df_auc <- read.table(paste0(path,tissue_name,"_auroc.csv"),header = TRUE)
df_auc = df_auc %>% filter(gt_set %in% c("Top100","CellMarkerDB")) %>% filter(!Method %in% "HighlyVariableGenes")
df_auc$Method <- with(df_auc, reorder(Method, -AUROC, FUN = median))
df_auc$gt_set <- factor(df_auc$gt_set,levels = c("Top100","CellMarkerDB"))
levels(df_auc$gt_set) = c("Criterion1 - MaxFC", "Criterion2 - CellMarkerDB")

# Create the plot
fig <- ggplot(df_auc, aes(x = gt_set, y = AUROC, fill = Method)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(AUROC, 2)), position = position_dodge(width = 0.85), vjust = -0.25, size = 2) +
  theme_minimal() +
  labs(x = "Ground-Truth Genesets", y = "AUROC", fill = "Method") + coord_cartesian(ylim = c(0.5, 1)) +
  theme(legend.position = "bottom")  +  scale_fill_manual(values= coldef[names(coldef)%in%df_auc$Method])
fig + ggtitle("Lung")
```

# Fig - Enrichment Overlap of Prioritized Genes with CellMarker Database Confidence Markers
```{r}
path = "./benchmark_result/"
tissue_name = "marrow_facs"

library(Seurat)
cell_marker_db = readxl::read_xlsx("/data/ruiqi/local_marker/dataset/Cell_Marker/Cell_marker_All.xlsx") %>% filter(species == "Mouse") %>% 
  filter(tissue_class == "Bone marrow") %>% filter(!is.na(cellontology_id)) %>% 
  filter(!is.na(PMID)) %>% mutate(gene_name1 = marker) %>% mutate(gene_name2 = Symbol) %>% select(c("gene_name1","gene_name2"))

df_benchmark = read.table(paste0(path,tissue_name,"_benchmark_rank_table.csv"))

method = "lmd"
gene_bin = data.frame(gene = rownames(df_benchmark)[order(df_benchmark[,method])][1:1000])
gene_bin$freq = unlist(lapply(gene_bin$gene,function(i){
  id = which(grepl(paste0("^", i, "$"), cell_marker_db$gene_name1, ignore.case = TRUE) + grepl(paste0("^", i, "$"), cell_marker_db$gene_name2, ignore.case = TRUE) >=1)
  return(length(id))
}) )
gene_bin$'freq_class' = cut(gene_bin$freq, breaks = c(-Inf,1,3,Inf), labels = c("none", "low", "high"), right = FALSE)

gene_bin$bin <- cut(seq(1:nrow(gene_bin)), breaks = 40, labels = FALSE)
gene_bin$'bin_label' = paste0(nrow(gene_bin)/max(gene_bin$bin)*(gene_bin$bin-1)+1,"-",nrow(gene_bin)/max(gene_bin$bin)*(gene_bin$bin))
gene_bin$'bin_label' = factor(gene_bin$'bin_label',levels = unique(gene_bin$'bin_label'))

gene_freq_prop <- gene_bin %>%
  group_by(bin_label, freq_class) %>%
  summarise(n = n()) %>%
  mutate(freq = n / sum(n))
gene_freq_prop$freq_class = factor(gene_freq_prop$freq_class,levels = c("none","low","high"),labels = c("None(=0)","Low(1,2)","High(>=3)"))

coldef = setNames(c("gray71","firebrick1","firebrick4"),levels(gene_freq_prop$freq_class))

fig = ggplot(gene_freq_prop, aes(fill=freq_class, y=freq, x=bin_label)) +
  geom_bar(position="fill", stat="identity") +
  ylab("Frequency") +
  xlab("Gene Rank") +
  labs(fill = "Confidence") +
  scale_fill_manual(values= coldef) +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

fig
```
```{r}
genes = c("Ctla2a","Fpr2","Mmp8")
pl = lapply(genes,function(g) FeaturePlot(tiss, g, order = TRUE) + labs(color = "Expression") + ggtitle(sprintf("%s (rank %d)",g,which(gene_bin == g))))
fig = cowplot::plot_grid(plotlist = pl, ncol = 3)
fig
```

@@

df_benchmark = read.table(paste0(path,tissue_name,"_benchmark_rank_table.csv"))

method_vs = "lmd"
method_vs_set = c("hotspot","haystack","wilcox_default")
pl = lapply(method_vs_set,function(method){
  p = ggplot(df_benchmark, aes(x=!!as.name(method), y=!!as.name(method_vs))) + geom_point(size = 1,col = "blue") +
    geom_abline(intercept = 0, slope = 1, col = "grey", linetype = "dashed") + scale_x_log10(breaks = 10^(0:4), labels = expression(10^0, 10^1, 10^2, 10^3, 10^4)) +
    scale_y_log10(breaks = 10^(0:4), labels = expression(10^0, 10^1, 10^2, 10^3, 10^4)) +
    expand_limits(x = c(1, 10^4), y = c(1, 10^4)) +
    labs(x = paste0(method_fullname[method]," Rank"), y = paste0(method_fullname[method_vs]," Rank")) + theme_minimal()

  # annotate gene labels
  library(ggrepel)
  df_label = data.frame(df_benchmark[,c(method,method_vs)],label = rownames(df_benchmark))
  sub = c(which(df_label[,method] <= 100 & df_label[,method_vs] > 500),
          which(df_label[,method] > 500 & df_label[,method_vs] <= 100) )
  df_label = df_label[sub,]
  df_label = df_label[order(df_label[,1]),]
  p = p + geom_text_repel(data = df_label, aes(label=label),col = "red",arrow = arrow(type = "closed", length = unit(0.01, "inches")),max.overlaps = 200)
  p
})
fig = cowplot::plot_grid(plotlist = pl, ncol = length(method_vs_set))
fig
```
```{r}
sub = do.call(c,lapply(method_vs_set,function(method){
  sub = c(which(df_benchmark[,method] <= 100 & df_benchmark[,method_vs] > 500),
          which(df_benchmark[,method] > 500 & df_benchmark[,method_vs] <= 100) )
  sub
}))
df_label_all = df_benchmark[unique(sub),c(method_vs_set,method_vs)]
df_label_all$'legend' = sapply(seq(nrow(df_label_all)),function(i){
  paste(paste(method_fullname[colnames(df_label_all)[c(4,1:3)]],df_label_all[i,c(4,1:3)],sep = ":"),collapse = "\n")
})

g = c("Mogat2","Vpreb2","Cd19","Mup3","Fyb","Naaa")
pl = lapply(g,function(x){
  FeaturePlot(tiss,features = x,order =TRUE) + annotation_custom(grob = grid::textGrob(df_label_all[x,"legend"], x = 1, y = 1, just = c("right", "top"),gp = grid::gpar(col = "red", fontsize = 10)))
})
fig = cowplot::plot_grid(plotlist = pl,ncol = 3)
fig
```

@@

# Fig - Module HeatMap
```{r}
load("./marrow_result/module_result.rdata")
module_color = setNames(colorRampPalette(brewer.pal(12, "Paired"))(nlevels(gene_partition)),levels(gene_partition))
celltype_color = setNames(colorRampPalette(brewer.pal(9, "Set1"))(length(unique(cell_label))),unique(cell_label))

p = pheatmap(as.matrix(dist),
              annotation_col = data.frame(Module = gene_partition),
              cluster_rows = gene_hree, 
              cluster_cols = gene_hree,
              ann_colors = list(Module = module_color),
              treeheight_row = 0,
              col=colorRampPalette(c("red","white","blue4"))(99),
              show_colnames = FALSE, 
              show_rownames = FALSE,
              annotation_legend = FALSE,
              # main = paste(distance_method,
              #              clustering_method,sep = "-"),
              silent = TRUE)
as.ggplot(p)
```
# Fig - Module Jaccard
```{r}
# Heatmap
pheatmap(jaccard_index, 
         cluster_rows=FALSE, cluster_cols=FALSE, 
         scale = "none", 
         color = colorRampPalette(rev(c("firebrick3", "white", "navy")))(100))
```
```{r}
# Bipartite Plot
df_edge <- as.data.frame(as.table(jaccard_index))
colnames(df_edge) = c("from","to","weight")
df_edge <- subset(df_edge, weight > 0.4)
df_edge$width = ifelse(df_edge$weight > 0.8,2,0.5)
df_node = data.frame(name=c(names(module_color),names(celltype_color)),color = c(module_color,celltype_color))
df_node$type = ifelse(df_node$name %in% names(module_color),TRUE,FALSE)

@@

plot(g, layout=l, vertex.size=2, vertex.label=ifelse(V(g)$type, V(g)$name, NA), vertex.frame.color = NA, asp=0.2, 
     vertex.label.cex=0.5,
     vertex.label.dist=-1,
     vertex.label.degree=pi/2)
coords = as.data.frame(l) %>% filter(V2 == 0) %>% mutate(labels = names(celltype_color))
text(x = coords$V1, y = coords$V2, labels = coords$labels, srt = 90, adj = c(1.5, 0.5),cex = 0.5,col = "black")
# Add legend for colors
legend("bottom", legend=names(celltype_color), fill=celltype_color, bty="n", cex=0.5)
```
# Fig - Module TSNE
```{r}
pl_module = lapply(levels(gene_partition),function(module){
  FeaturePlot_custom(value = cell_block[,module], coord = visual_space, value_name = "Module Score",title_name = sprintf("Module %s (%d genes)",module, sum(gene_partition == module)))
})
names(pl_module) = levels(gene_partition)
legend <- get_legend(pl_module[[1]])
prow <- cowplot::plot_grid(plotlist = lapply(pl_module,function(x) x + theme(legend.position="none")), ncol = 10)
pdf(width = 30, height = 18)
cowplot::plot_grid(prow, legend, rel_widths = c(10, .2))
dev.off()
```
# Fig - Module-CellType
```{r}
jaccard_thred = 0.4
one_hot_matrix <- sapply(unique(cell_label), function(x) as.integer(cell_label == x))
# Get CellType One-hot plot
pl_ct = lapply(colnames(one_hot_matrix),function(ct){
  FeaturePlot_custom(value = as.factor(one_hot_matrix[,ct]), coord = visual_space, value_name = "Indicator",title_name = ct)
})
names(pl_ct) = colnames(one_hot_matrix)

>>>>

df_benchmark = read.table(paste0(path,tissue_name,"_benchmark_rank_table.csv"))
method_ls = colnames(df_benchmark)
method_fullname = setNames(c("LMD","singleCellHaystack","Hotspot","Marcopolo","SEMITONES","Seurat v3 default", "Seurat v3 Wilcoxon unfiltered","HighlyVariableGenes"),method_ls)
coldef = setNames(
  colorRampPalette(brewer.pal(9, "Set1"))(length(method_fullname)),
  method_fullname)
```
```{r}
df_auc <- read.table(paste0(path,tissue_name,"_auroc.csv"),header = TRUE)
df_auc = df_auc %>% filter(gt_set %in% c("Top100","CellMarkerDB")) %>% filter(!Method %in% "HighlyVariableGenes")
df_auc$Method <- with(df_auc, reorder(Method, -AUROC, FUN = median))
df_auc$gt_set <- factor(df_auc$gt_set,levels = c("Top100","CellMarkerDB"))
levels(df_auc$gt_set) = c("Criterion1 - MaxFC", "Criterion2 - CellMarkerDB")

# Create the plot
fig <- ggplot(df_auc, aes(x = gt_set, y = AUROC, fill = Method)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = round(AUROC, 2)), position = position_dodge(width = 0.85), vjust = -0.25, size = 2) +
  theme_minimal() +
  labs(x = "Ground-Truth Genesets", y = "AUROC", fill = "Method") + coord_cartesian(ylim = c(0.5, 1)) +
  theme(legend.position = "bottom")  +  scale_fill_manual(values= coldef[names(coldef)%in%df_auc$Method])
fig + ggtitle(tissue_name)
```

<!-- # Fig - Enrichment Overlap of Prioritized Genes with CellMarker Database Confidence Markers -->
<!-- ```{r} -->
<!-- path = "./benchmark_result/" -->
<!-- tissue_name = "marrow_facs" -->

<!-- library(Seurat) -->
<!-- cell_marker_db = readxl::read_xlsx("/data/ruiqi/local_marker/dataset/Cell_Marker/Cell_marker_All.xlsx") %>% filter(species == "Mouse") %>%  -->
<!--   filter(tissue_class == "Bone marrow") %>% filter(!is.na(cellontology_id)) %>%  -->
<!--   filter(!is.na(PMID)) %>% mutate(gene_name1 = marker) %>% mutate(gene_name2 = Symbol) %>% select(c("gene_name1","gene_name2")) -->

<!-- df_benchmark = read.table(paste0(path,tissue_name,"_benchmark_rank_table.csv")) -->

<!-- method = "lmd" -->
<!-- gene_bin = data.frame(gene = rownames(df_benchmark)[order(df_benchmark[,method])][1:1000]) -->
<!-- gene_bin$freq = unlist(lapply(gene_bin$gene,function(i){ -->
<!--   id = which(grepl(paste0("^", i, "$"), cell_marker_db$gene_name1, ignore.case = TRUE) + grepl(paste0("^", i, "$"), cell_marker_db$gene_name2, ignore.case = TRUE) >=1) -->
<!--   return(length(id)) -->
<!-- }) ) -->
<!-- gene_bin$'freq_class' = cut(gene_bin$freq, breaks = c(-Inf,1,3,Inf), labels = c("none", "low", "high"), right = FALSE) -->

<!-- gene_bin$bin <- cut(seq(1:nrow(gene_bin)), breaks = 40, labels = FALSE) -->
<!-- gene_bin$'bin_label' = paste0(nrow(gene_bin)/max(gene_bin$bin)*(gene_bin$bin-1)+1,"-",nrow(gene_bin)/max(gene_bin$bin)*(gene_bin$bin)) -->
<!-- gene_bin$'bin_label' = factor(gene_bin$'bin_label',levels = unique(gene_bin$'bin_label')) -->

<!-- gene_freq_prop <- gene_bin %>% -->
<!--   group_by(bin_label, freq_class) %>% -->
<!--   summarise(n = n()) %>% -->
<!--   mutate(freq = n / sum(n)) -->
<!-- gene_freq_prop$freq_class = factor(gene_freq_prop$freq_class,levels = c("none","low","high"),labels = c("None(=0)","Low(1,2)","High(>=3)")) -->

<!-- coldef = setNames(c("gray71","firebrick1","firebrick4"),levels(gene_freq_prop$freq_class)) -->

<!-- fig = ggplot(gene_freq_prop, aes(fill=freq_class, y=freq, x=bin_label)) + -->
<!--   geom_bar(position="fill", stat="identity") + -->
<!--   ylab("Frequency") + -->
<!--   xlab("Gene Rank") + -->
<!--   labs(fill = "Confidence") + -->
<!--   scale_fill_manual(values= coldef) + -->
<!--   theme_minimal() +  -->
<!--   theme(axis.text.x = element_text(angle = 45, hjust = 1)) -->

<!-- fig -->
<!-- ``` -->
<!-- ```{r} -->
<!-- genes = c("Ctla2a","Fpr2","Mmp8") -->
<!-- pl = lapply(genes,function(g) FeaturePlot(tiss, g, order = TRUE) + labs(color = "Expression") + ggtitle(sprintf("%s (rank %d)",g,which(gene_bin == g)))) -->
<!-- fig = cowplot::plot_grid(plotlist = pl, ncol = 3) -->
<!-- fig -->
<!-- ``` -->

@@

df_benchmark = read.table(paste0(path,tissue_name,"_benchmark_rank_table.csv"))
method_vs = "lmd"
method_vs_set = c("wilcox_default","hotspot","marcopolo","semi","haystack")
```
```{r}
sub = do.call(c,lapply(method_vs_set,function(method){
  sub = c(which(df_benchmark[,method] <= 100 & df_benchmark[,method_vs] > 500),
          which(df_benchmark[,method] > 500 & df_benchmark[,method_vs] <= 100) )
  sub
}))
df_label_all = df_benchmark[unique(sub),c(method_vs,method_vs_set)]
df_label_all$'legend' = sapply(seq(nrow(df_label_all)),function(i){
  paste(paste(method_fullname[colnames(df_label_all)],df_label_all[i,],sep = ":"),collapse = "\n")
})
g = c("Mogat2","Vpreb2","Cd19","Abca13","Il2rb","Mup3","Fyb","Naaa","Zf12","Phgdh")
pl = lapply(g,function(x){
  FeaturePlot(tiss,features = x,order =TRUE) + annotation_custom(grob = grid::textGrob(df_label_all[x,"legend"], x = 1, y = 1, just = c("right", "top"),gp = grid::gpar(col = "red", fontsize = 10)))
})
fig = cowplot::plot_grid(plotlist = pl,ncol = length(method_vs_set))
fig
```
```{r}
pl_rank = lapply(method_vs_set,function(method){
  df_label = data.frame(df_benchmark[,c(method,method_vs)],label = rownames(df_benchmark))
  df_label[c(which(df_label[,method] <= 100 & df_label[,method_vs] > 500)),"color"] = sprintf("Favor by %s (rank <= 100)",method)
  df_label[c(which(df_label[,method] > 500 & df_label[,method_vs] <= 100) ),"color"] = sprintf("Favor by %s (rank <= 100)",method_vs)
  df_label$'color' = as.factor(df_label$'color')
  p = ggplot(df_label, aes(x=!!as.name(method), y=!!as.name(method_vs),color = color)) + geom_point(size = 1) + 
  scale_color_manual(values = c("red", "blue", "grey50"),
                     breaks = levels(df_label$'color')) + 
    geom_abline(intercept = 0, slope = 1, col = "grey", linetype = "dashed") + scale_x_log10(breaks = 10^(0:4), labels = expression(10^0, 10^1, 10^2, 10^3, 10^4)) +
    scale_y_log10(breaks = 10^(0:4), labels = expression(10^0, 10^1, 10^2, 10^3, 10^4)) +
    expand_limits(x = c(1, 10^4), y = c(1, 10^4)) +
    labs(x = paste0(method_fullname[method]," Rank"), y = paste0(method_fullname[method_vs]," Rank"), color = "Highlighted Genes") + theme_minimal() 
  # annotate gene labels
  # library(ggrepel)
  p = p + geom_text(data = df_label %>% filter(!is.na(color)) %>% filter(label %in% g), aes(label=label))
  p
})
fig = cowplot::plot_grid(plotlist = pl_rank, ncol = length(method_vs_set))
fig
```

@@

# Fig - Module HeatMap
```{r}
load("./marrow_result/module_result.rdata")
source("./LMD_function.R", echo = F)
library(RColorBrewer)
library(dplyr)
module_color = setNames(colorRampPalette(brewer.pal(12, "Paired"))(nlevels(gene_partition)),levels(gene_partition))
celltype_color = setNames(colorRampPalette(brewer.pal(9, "Set1"))(length(unique(cell_label))),unique(cell_label))

p = pheatmap(as.matrix(dist),
              annotation_col = data.frame(Module = gene_partition),
              cluster_rows = gene_hree, 
              cluster_cols = gene_hree,
              ann_colors = list(Module = module_color),
              treeheight_row = 0,
              col=colorRampPalette(c("red","white","blue4"))(99),
              show_colnames = FALSE, 
              show_rownames = FALSE,
              annotation_legend = FALSE,
              # main = paste(distance_method,
              #              clustering_method,sep = "-"),
              silent = TRUE)
as.ggplot(p)
```
# Fig - Module Jaccard
```{r}
# Heatmap
pheatmap(jaccard_index, 
         cluster_rows=FALSE, cluster_cols=FALSE, 
         scale = "none", 
         color = colorRampPalette(rev(c("firebrick3", "white", "navy")))(100))
```
```{r}
# Bipartite Plot
jaccard_thred = 0.4

library(igraph)
library("grid") 
library("gridExtra")

df_edge <- as.data.frame(as.table(jaccard_index))
colnames(df_edge) = c("from","to","weight")
df_edge <- subset(df_edge, weight > jaccard_thred)
df_edge$width = ifelse(df_edge$weight > 0.8,2,0.5)
df_node = data.frame(name=c(names(module_color),names(celltype_color)),color = c(module_color,celltype_color))
df_node$type = ifelse(df_node$name %in% names(module_color),TRUE,FALSE)

# Define specific color for module
rownames(df_node) = df_node$name
ct_module = names(which(apply(jaccard_index,2,max) > jaccard_thred))
ct_subtype_module = c(4,5,6,30,39,42,43)
ct_multype_module = c(2,13,19,33,36,54)
cc_module = c(16,17,18,31)
df_node[names(module_color),"color"] = "grey"
df_node[ct_module,"color"] = "red"
df_node[ct_multype_module,"color"] = "purple"
df_node[ct_subtype_module,"color"] = "yellow"
df_node[cc_module,"color"] = "green"

@@

plot(g, layout=l, vertex.size=2, vertex.label=ifelse(V(g)$type, V(g)$name, NA), vertex.frame.color = NA, asp=0.2, 
     vertex.label.cex=0.5,
     vertex.label.dist=-1,
     vertex.label.degree=pi/2)

# Create Node Legend & Edge Legend
color_label = c("green" = "cell cycle",purple = "multi cell type",red = "cell type",yellow = "cell subtype")
df_node$subtype = color_label[df_node$color]

p <- ggplot(df_node %>% filter(type), aes(x = 0, y = 0,color = subtype)) + geom_point(size = 7) + scale_color_manual(values= setNames(names(color_label),color_label)) + theme_minimal() + labs(color = "Module Type") + theme(legend.direction="horizontal")
grid.newpage()
grid.draw(get_legend(p))

p <- ggplot(df_node %>% filter(!type), aes(x = 0, y = 0,color = name)) + geom_point(size = 7,shape = 15) + scale_color_manual(values= df_node %>% filter(!type) %>% pull(color,name)) + theme_minimal() + labs(color = "Cell Type") + theme(legend.direction="horizontal")
grid.newpage()
grid.draw(get_legend(p))
```
# Fig - Module TSNE
```{r}
pl_module = lapply(levels(gene_partition),function(module){
  FeaturePlot_custom(value = cell_block[,module], coord = visual_space, value_name = "Module Score",title_name = sprintf("Module %s (%d genes)",module, sum(gene_partition == module)))
})
names(pl_module) = levels(gene_partition)
legend <- get_legend(pl_module[[1]])
prow <- cowplot::plot_grid(plotlist = lapply(pl_module,function(x) x + theme(legend.position="none")), ncol = 10)
pdf(width = 30, height = 18)
cowplot::plot_grid(prow, legend, rel_widths = c(10, .2))
dev.off()
```
# Fig - Module-CellType
```{r}
jaccard_thred = 0.4
one_hot_matrix <- sapply(unique(cell_label), function(x) as.integer(cell_label == x))
# Get CellType One-hot plot
pl_ct = lapply(colnames(one_hot_matrix),function(ct){
  FeaturePlot_custom(value = as.factor(one_hot_matrix[,ct]), coord = visual_space, value_name = "Indicator",title_name = ct)
})
names(pl_ct) = colnames(one_hot_matrix)
